The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
edit fitness P4

Social scale is another major consideration for social network analysis, especially when thinking about different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015). It is a common trope that individuals need to be associating in order to interact and an assumption that proximity is proxy for interacting (Farine, 2015). For instance, baboons need to be in proximity in order to groom each other, but this trope is only thinking about interactions that humans are most prone to seeing and valuing with our bias toward visual perception. Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015). With improved and more affordable technology, we can now start to understand some of these interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017). The multilayer network framework further enables researchers to look at these different social scales and test how good a proxy proximity is for various forms of interacting in a holistic way.

>>>>

Social scale is another major consideration for social network analysis, especially in the context of different types of interactions and associations in the same analysis (Carter, Lee, & Marshall, 2015; Castles et al., 2014; Farine, 2015). It is a common trope that individuals must be associating to interact and most studies therefore assume that proximity is proxy for interacting (Farine, 2015). For instance, baboons need to be in proximity in order to groom each other, but this trope highlights human bias toward interactions that can be readily observed in the field. Animals have certain interactions that do not require proximity such as long-distance vocalization and olfactory signals (Carter et al., 2015). With the advancement of bio-logging technology, our ability to record social interactions that do not require proximity, particularly long-distance communication networks with devices like microphone arrays (Snijders & Naguib, 2017). The multilayer network framework further enables researchers to examine the relationship between social phenotypes and fitness across social scales and to test how good a social proximity is for various forms of interacting in a holistic way.
